# Practical Machine Learning Project

## Summary

This project is to build a model to predict the type of activities performed by participants.

The training data for this project are available here:
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here:
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

## Load and Clean Data

```{r, message=FALSE, warning=FALSE}
library(caret)
training<-read.csv('pml-training.csv',header= TRUE)
testing<-read.csv('pml-testing.csv',header=TRUE)
#remove NAs
training<-training[,colSums(is.na(training)) == 0]
#remove near zero variance
nearZero<-nearZeroVar(training, saveMetrics=TRUE)
training<-training[, nearZero$nzv==FALSE]
#remove unrelevant columns
training<-training[,7:ncol(training)]
```

## Build the model using random forest

```{r, message=FALSE, warning=FALSE}
set.seed(1990)
inTrain<-createDataPartition(training$classe,p=0.7,list=FALSE)
train<-training[inTrain,]
test<-training[-inTrain,]
#set the cross-validation
ctrl<-trainControl(method="cv", number=5, allowParallel=TRUE)
modFit<-train(classe ~ ., data=train, method="rf", trControl=ctrl)
modFit$finalModel
```

## Test&Out-of-Sample Error

```{r}
testingPredict<-predict(modFit, test)
cm<-confusionMatrix(testingPredict,test$classe)
cm
outError<-1-sum(diag(cm$table))/sum(cm$table)
outError
```
The out of sample error is less than 1%

## Predictions

```{r}
predict20 <- predict(modFit, testing)
print( predict20 )
```
The results are all correct